Results

### 2021-07-27 Analysis/03_Summarise_results.Rmd
Added fancy plots

```{r, fig.width = 8, fig.height = 12}
fancy.plot(scaled_results, col = c("blue", "orange"))
```

Here is the visualisation of the results per stressor and per metric.

@@

<!-- # Sanity checking

This is what is happening in one simulation (e.g. for alpha)
 -->

```{r, eval = FALSE, echo = FALSE}
## Get the result table
results_table <- facilitation$results_table

## Get the alpha metric
alpha_results <- results_table[, grep("alpha", colnames(results_table))]

## Get the results of the first simulation
first_sim_alpha <- alpha_results[1,]

## Get the data removal from the first simulation for 40% removal
first_sim <- facilitation$output_save[[1]]
random_sim_40 <- first_sim$reductions[[2]][, "random"]
stress_sim_40 <- first_sim$reductions[[2]][, "stressor"]

par(mfrow = c(1, 2))
plot(first_sim$trait_space, col = "grey", pch = 19, main = "stressor")
points(first_sim$trait_space[stress_sim_40, ], col = "orange", pch = 19)
plot(first_sim$trait_space, col = "grey", pch = 19, main = "random")
points(first_sim$trait_space[random_sim_40, ], col = "blue", pch = 19)

## Recalculate the metrics
tree <- hclust(dist(first_sim$trait_space), method = "average")
BAT::alpha(t(first_sim$reductions[[2]]), tree)
#          Richness
# random   65.29787
# stressor 46.76265
first_sim_alpha[3:4] # OK
```

>>>>

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"))
```
Figure X1: Simulation results: the y axes represent the different metrics tested (sorted by categories). The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors. Negative and positive values signify a decrease/increase in the metric score. The dots represent the median metric value, the full line their 50% confidence interval (CI) and the dashed line their 95% CI. The colours are just here to visually separate the metrics rows but the colour gradient within each row corresponds to a removal of respectively 80%, 60%, 40% and 20% of the data (from top to bottom).

>TG: Here is the visualisation of the results per stressor and per metric.

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"), lm = model_fits, null = null_differences)
```
Figure X2: See above + Grey lines in the background are a fitted linear model on the scaled metric score function of removal amount and the value displayed is the adjusted R^2 from each of these models. Dashed grey lines represent non-significant models (slope or/and intercept). The grey line plots represent (CI + median) represent distribution of metrics scores not clearly different from the random metric scores (paired t-test p value > 0.05).

>TG: Here is the visualisation of the results per stressor and per metric.

@@
